Weighted Model Counting Without Parameter Variables

### 2021-06-17 doc/SAT_long_talk/box.tex
Slides for the long SAT talk are almost finished

% Created by tikzDevice version 0.12.3.1 on 2021-06-14 12:12:55
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (303.53,224.04);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (303.53,224.04);
\end{scope}
\begin{scope}
\path[clip] ( 40.51, 33.38) rectangle (298.03,218.54);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.51, 33.38) rectangle (298.03,218.54);
\definecolor{drawColor}{gray}{0.87}

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 73.27) --
	(298.03, 73.27);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,136.86) --
	(298.03,136.86);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,200.45) --
	(298.03,200.45);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 41.48) --
	(298.03, 41.48);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,105.07) --
	(298.03,105.07);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,168.66) --
	(298.03,168.66);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 70.22, 33.38) --
	( 70.22,218.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] (119.75, 33.38) --
	(119.75,218.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] (169.27, 33.38) --
	(169.27,218.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] (218.80, 33.38) --
	(218.80,218.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] (268.32, 33.38) --
	(268.32,218.54);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.94,178.58) -- ( 60.94,327.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.94, 52.60) -- ( 60.94, 42.30);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 52.58,178.58) --
	( 52.58, 52.60) --
	( 69.30, 52.60) --
	( 69.30,178.58) --
	( 52.58,178.58) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 52.58, 89.33) -- ( 69.30, 89.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.51, 92.86) -- ( 79.51,158.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.51, 45.93) -- ( 79.51, 41.79);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 71.15, 92.86) --
	( 71.15, 45.93) --
	( 87.87, 45.93) --
	( 87.87, 92.86) --
	( 71.15, 92.86) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 71.15, 53.43) -- ( 87.87, 53.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (110.46,185.67) -- (110.46,366.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (110.46, 54.83) -- (110.46, 42.49);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (102.11,185.67) --
	(102.11, 54.83) --
	(118.82, 54.83) --
	(118.82,185.67) --
	(102.11,185.67) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (102.11, 92.03) -- (118.82, 92.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.03,160.26) -- (129.03,292.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.03, 50.38) -- (129.03, 42.21);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (120.68,160.26) --
	(120.68, 50.38) --
	(137.39, 50.38) --
	(137.39,160.26) --
	(120.68,160.26) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (120.68, 66.91) -- (137.39, 66.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.99,185.77) -- (159.99,366.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.99, 54.83) -- (159.99, 42.49);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (151.63,185.77) --
	(151.63, 54.83) --
	(168.34, 54.83) --
	(168.34,185.77) --
	(151.63,185.77) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (151.63, 92.03) -- (168.34, 92.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.56,160.26) -- (178.56,292.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.56, 50.38) -- (178.56, 42.21);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (170.20,160.26) --
	(170.20, 50.38) --
	(186.91, 50.38) --
	(186.91,160.26) --
	(170.20,160.26) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (170.20, 66.91) -- (186.91, 66.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.51,164.59) -- (209.51,306.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.51, 50.38) -- (209.51, 42.18);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (201.15,164.59) --
	(201.15, 50.38) --
	(217.87, 50.38) --
	(217.87,164.59) --
	(201.15,164.59) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (201.15, 75.53) -- (217.87, 75.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.08, 99.15) -- (228.08,158.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.08, 45.93) -- (228.08, 41.79);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (219.72, 99.15) --
	(219.72, 45.93) --
	(236.44, 45.93) --
	(236.44, 99.15) --
	(219.72, 99.15) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (219.72, 54.19) -- (236.44, 54.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] (268.32,132.06) -- (268.32,244.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (268.32, 48.15) -- (268.32, 41.98);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (251.61,132.06) --
	(251.61, 48.15) --
	(285.03, 48.15) --
	(285.03,132.06) --
	(251.61,132.06) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (251.61, 69.27) -- (285.03, 69.27);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 33.38) rectangle (298.03,218.54);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.30}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,165.63) {4000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.70}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,168.66) --
	( 40.51,168.66);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 70.22, 30.63) --
	( 70.22, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (119.75, 30.63) --
	(119.75, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (169.27, 30.63) --
	(169.27, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (218.80, 30.63) --
	(218.80, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (268.32, 30.63) --
	(268.32, 33.38);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 70.22, 22.37) {\texttt{bklm16}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (119.75, 22.37) {\texttt{cd05}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (169.27, 22.37) {\texttt{cd06}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (218.80, 22.37) {\texttt{d02}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (268.32, 22.37) {\texttt{sbk05}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,125.96) {Variables};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (123.14,  5.50) rectangle (215.40, -2.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (128.64,  5.50) rectangle (143.10, 19.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (135.87,  6.95) --
	(135.87,  9.11);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (135.87, 16.34) --
	(135.87, 18.51);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (130.45,  9.11) rectangle (141.29, 16.34);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (130.45, 12.73) --
	(141.29, 12.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (177.58,  5.50) rectangle (192.04, 19.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (184.81,  6.95) --
	(184.81,  9.11);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (184.81, 16.34) --
	(184.81, 18.51);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (179.39,  9.11) rectangle (190.23, 16.34);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (179.39, 12.73) --
	(190.23, 12.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (148.60,  9.70) {before};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (197.54,  9.70) {after};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-06-17 09:56:52
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\end{document}
re}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (180.67,224.04);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (180.68,224.04);
\end{scope}
\begin{scope}
\path[clip] ( 40.51, 33.38) rectangle (175.17,218.54);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.51, 33.38) rectangle (175.17,218.54);
\definecolor{drawColor}{gray}{0.87}

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 73.27) --
	(175.17, 73.27);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,136.86) --
	(175.17,136.86);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,200.45) --
	(175.17,200.45);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 41.48) --
	(175.17, 41.48);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,105.07) --
	(175.17,105.07);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,168.66) --
	(175.17,168.66);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 56.05, 33.38) --
	( 56.05,218.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 81.95, 33.38) --
	( 81.95,218.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] (107.84, 33.38) --
	(107.84,218.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] (133.74, 33.38) --
	(133.74,218.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] (159.64, 33.38) --
	(159.64,218.54);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.19,178.58) -- ( 51.19,327.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.19, 52.60) -- ( 51.19, 42.30);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 46.82,178.58) --
	( 46.82, 52.60) --
	( 55.56, 52.60) --
	( 55.56,178.58) --
	( 46.82,178.58) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 46.82, 89.33) -- ( 55.56, 89.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.90, 92.86) -- ( 60.90,158.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.90, 45.93) -- ( 60.90, 41.79);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 56.53, 92.86) --
	( 56.53, 45.93) --
	( 65.27, 45.93) --
	( 65.27, 92.86) --
	( 56.53, 92.86) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 56.53, 53.43) -- ( 65.27, 53.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.09,185.67) -- ( 77.09,366.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.09, 54.83) -- ( 77.09, 42.49);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 72.72,185.67) --
	( 72.72, 54.83) --
	( 81.46, 54.83) --
	( 81.46,185.67) --
	( 72.72,185.67) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 72.72, 92.03) -- ( 81.46, 92.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.80,160.26) -- ( 86.80,292.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.80, 50.38) -- ( 86.80, 42.21);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 82.43,160.26) --
	( 82.43, 50.38) --
	( 91.17, 50.38) --
	( 91.17,160.26) --
	( 82.43,160.26) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 82.43, 66.91) -- ( 91.17, 66.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (102.99,185.77) -- (102.99,366.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (102.99, 54.83) -- (102.99, 42.49);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 98.62,185.77) --
	( 98.62, 54.83) --
	(107.36, 54.83) --
	(107.36,185.77) --
	( 98.62,185.77) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 98.62, 92.03) -- (107.36, 92.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] (112.70,160.26) -- (112.70,292.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] (112.70, 50.38) -- (112.70, 42.21);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (108.33,160.26) --
	(108.33, 50.38) --
	(117.07, 50.38) --
	(117.07,160.26) --
	(108.33,160.26) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (108.33, 66.91) -- (117.07, 66.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (128.88,164.59) -- (128.88,306.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (128.88, 50.38) -- (128.88, 42.18);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (124.51,164.59) --
	(124.51, 50.38) --
	(133.25, 50.38) --
	(133.25,164.59) --
	(124.51,164.59) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (124.51, 75.53) -- (133.25, 75.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (138.60, 99.15) -- (138.60,158.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] (138.60, 45.93) -- (138.60, 41.79);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (134.23, 99.15) --
	(134.23, 45.93) --
	(142.97, 45.93) --
	(142.97, 99.15) --
	(134.23, 99.15) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (134.23, 54.19) -- (142.97, 54.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.64,132.06) -- (159.64,244.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.64, 48.15) -- (159.64, 41.98);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (150.90,132.06) --
	(150.90, 48.15) --
	(168.38, 48.15) --
	(168.38,132.06) --
	(150.90,132.06) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (150.90, 69.27) -- (168.38, 69.27);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 33.38) rectangle (175.17,218.54);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
\definecolor{drawColor}{gray}{0.30}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,165.63) {4000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
\definecolor{drawColor}{gray}{0.70}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,168.66) --
	( 40.51,168.66);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 56.05, 30.63) --
	( 56.05, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 81.95, 30.63) --
	( 81.95, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (107.84, 30.63) --
	(107.84, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (133.74, 30.63) --
	(133.74, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (159.64, 30.63) --
	(159.64, 33.38);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.05, 22.37) {\texttt{bklm16}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 81.95, 22.37) {\texttt{cd05}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (107.84, 22.37) {\texttt{cd06}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (133.74, 22.37) {\texttt{d02}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (159.64, 22.37) {\texttt{sbk05}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,125.96) {Variables};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 61.71,  5.50) rectangle (153.97, -2.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 67.21,  5.50) rectangle ( 81.67, 19.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 74.44,  6.95) --
	( 74.44,  9.11);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 74.44, 16.34) --
	( 74.44, 18.51);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 69.02,  9.11) rectangle ( 79.86, 16.34);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 69.02, 12.73) --
	( 79.86, 12.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (116.15,  5.50) rectangle (130.61, 19.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (123.38,  6.95) --
	(123.38,  9.11);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (123.38, 16.34) --
	(123.38, 18.51);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (117.96,  9.11) rectangle (128.80, 16.34);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (117.96, 12.73) --
	(128.80, 12.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 87.17,  9.70) {before};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (136.11,  9.70) {after};
\end{scope}
\end{tikzpicture}
